---
exclude_jquery: true
title: Śākta
menu: main
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(here)
library(DT)

manuscript_meta <- read_csv(here("static", "manuscripts", "manuscript_meta.csv"))
```

<main class="main-page-restrict-width">
::: {.row .manuscript-list-page-header}
::: {.col-sm-12}
# Śākta manuscripts
:::
:::

::: {.row}
::: {.col-lg-9 .col-md-9 .col-sm-6}
- This will be the front page to the section of the site where Hindu and Buddhist manuscripts associated with the Śākta Traditions research programme can be browsed
:::

::: {.col-lg-3 .col-md-3 .col-sm-6}
::: {.embed-responsive .embed-responsive-16by9}
<iframe class='embed-responsive-item featured-work-graphic' src='https://player.vimeo.com/video/376577532' allow="fullscreen" allowfullscreen></iframe>
:::
<!-- end column -->
:::

<!-- end row -->
:::

</main>

<main class="manuscript-list">
::: {.row}
::: {.col-sm-12}
<br>

# Select a text

*Click the __Popular identifier__ to go to the content. Hover over a cell to see all its information. Search within a column by typing in the 'All' box.*

*You can also download this table:*

```{r}
df <- manuscript_meta %>% 
  select(-googlesheet_with_text, 
         -googlesheet_id, 
         -id) %>%
  arrange(desc(has_content), desc(Date_added)) %>% 
  mutate(Date_added = as.character(Date_added)) %>% 
  mutate(Identifier_popular = ifelse(has_content == "yes",
                                     str_c("<a href='/manuscripts/", Catalogue_id, "/'>", Identifier_popular, "</a>"),
                                     Identifier_popular)) %>% 
  mutate(Identifier_popular = str_c("<span class='pop-identifier'>", Identifier_popular, "</span>")) %>% 
  select(-has_content, -Date_added, -Catalogue_id, -website_photo_extension, -private_notes)

#across(-has_content, ~str_c("som))

df %>% 
  datatable(rownames = FALSE,
            escape = FALSE,
            colnames = c('Popular identifier' = 'Identifier_popular',
                         'Title: sanskrit' = 'Title_sanskrit',
                         'Title: transliteration' = 'Title_transliteration',
                         'Title: english translation' = 'Title_english',
                         'Current physical location' = 'Physical_location',
                         'Place of origin' = 'Origin_place',
                         'Transliterated by' = 'Transliterated_by',
                         'English translation by' = 'Translation_english_by',
                         'Danish translation by' = 'Translation_danish_by',
                         'Entry contains photos?' = 'has_photos',
                         'Entry contains text?' = 'has_text'),
            filter = 'top',
            class = 'row-border',
            elementId = "manuscriptListDT",
            extensions = 'Buttons',
            options = list(paging = FALSE, 
                           scrollX = TRUE,
                           keys = TRUE,
                           dom = 'Bfrtip',
                           buttons = c('csv', 'excel', 'print')
                           ))

```
<br>

:::
:::

</main>